Preregistration, design, IRB

### 2020-10-01 analysis/01_clean-data.Rmd
Update to use latest tidyverse conventions
list() instead of funs(); pivot_*() instead of gather() and spread()
Clean up code to work with dplyr 1.0 and friends

---
title: "Clean data"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

@@

            funs(factor(., levels = favorability, ordered = TRUE))) %>% 

@@

            funs(bin = fct_recode(., 

>>>>

---
title: "Clean data"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: show
editor_options: 
  chunk_output_type: console
---

@@

            list(~factor(., levels = favorability, ordered = TRUE))) %>% 

@@

            list(bin = ~fct_recode(., 

### 2020-10-01 analysis/02_analysis.Rmd
Clean up code to work with dplyr 1.0 and friends

@@

```{r causal-dag, fig.width=4.75, fig.height=2}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C") %>% 
  tidy_dagitty(layout = "sugiyama")

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

@@

```{r fig-likelihood-bars, fig.width=9, fig.height=4}
donate_summary <- results %>% 
  count(donate_likely) %>% 
  mutate(perc = n / sum(n)) %>% 
  mutate(highlight = ifelse(donate_likely %in% c("Extremely likely", "Somewhat likely"), TRUE, FALSE))

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_cols("blue")) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

```{r priors-likely, fig.width=2.75, fig.height=1.5, fig.align="center"}
likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
            fill = "grey80", color = "black") +
  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)
likely_theta

@@

```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

```{r priors-amounts, fig.width=8, fig.height=1.5}
amount_nu <- ggplot(data = tibble(x = c(0, 200)), aes(x = x)) +
  geom_area(stat = "function", fun = dexp, args = list(rate = 1/29), 
            fill = "grey80", color = "black") +
  labs(x = expression(Normality ~ parameter ~ (nu)), y = "Density") +
  annotate(geom = "label", x = 100, y = 0.009, 
           label = "Exponential(1/29)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5}
# This will generate a warning because unnest() puts the crackdown values into
# one column and we cheated by renaming issue and funding as crackdown, so it
# gets mad when combining the factors in crackdown with those in issue and
# funding. But because we only care about the diffs, we don't actually need the
# category labels here, so it's all good.
tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

```{r amount-effect-size, warning=FALSE}
# Effect size
# (μ₁ - μ₂) / sqrt( (σ₁² + σ₂²) / 2)
tidied_eff_size_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "cohen_d") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title = fct_inorder(title))

@@

ggplot(tidied_eff_size_amount, aes(x = .value, y = fct_rev(title))) +
  geom_halfeyeh(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0, size = 1) +
  geom_vline(xintercept = c(0.2, -0.2), linetype = "dotted", size = 0.5) +
  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
  coord_cartesian(xlim = c(-0.6, 0.6)) +
  labs(x = "Cohen's d (effect size)", y = NULL) +
  theme_ngos()
```

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3, fig.align = "center")
```

@@

```{r causal-dag, fig.width=4.75, fig.height=2, out.width="70%"}
theory_dag <- dagify(Y ~ I + C + F,
                     C ~ I + F,
                     outcome = "Y",
                     exposure = "C",
                     labels = c("Y" = "Outcome (Likelihood of donation & amount donated)", 
                                "C" = "Anti-NGO legal crackdown", 
                                "I" = "NGO issue area", 
                                "F" = "NGO funding source")) %>% 
  tidy_dagitty(layout = "sugiyama")

plot_dag <- ggplot(theory_dag, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_point(size = 6) +
  geom_dag_edges(start_cap = circle(4, "mm"),
                 end_cap = circle(4, "mm")) +
  geom_dag_text(size = pts(6), family = "Roboto Condensed", fontface = "bold") +
  geom_dag_label_repel(aes(label = label), size = pts(6), box.padding = 0.1, 
                       direction = "x", seed = 12345,
                       family = "Roboto Condensed", fontface = "plain") +
  labs(x = NULL) +
  theme_ngos() +
  theme(panel.grid = element_blank(),
        axis.title = element_blank(),
        axis.text = element_blank())

@@

```{r fig-likelihood-bars, fig.width=9, fig.height=4, out.width="80%"}
donate_summary <- results %>% 
  count(donate_likely) %>% 
  mutate(perc = n / sum(n)) %>% 
  mutate(highlight = ifelse(donate_likely %in% c("Extremely likely", "Somewhat likely"), TRUE, FALSE))

@@

```{r fig-amount-bars, fig.width=9, fig.height=2.75, out.width="80%"}
plot_amount_summary <- ggplot(results, aes(x = amount_donate)) +
  geom_histogram(bins = 20, fill = ngo_cols("blue")) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL) +
  theme_ngos() +
  theme(panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

@@

```{r priors-likely, fig.width=2.75, fig.height=1.5, out.width="50%"}
likely_theta <- ggplot(data = tibble(x = c(0, 1)), aes(x = x)) +
  geom_area(stat = "function", fun = dbeta, args = list(shape1 = 5, shape2 = 5), 
            fill = "grey80", color = "black") +
  labs(x = expression(Probability ~ of ~ being ~ likely ~ to ~ donate ~ (theta)), y = "Density") +
  annotate(geom = "label", x = 0.5, y = 1, label = "Beta(5, 5)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)
likely_theta

@@

```{r plot-likely-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5, out.width="90%"}
tidied_diffs_likely <- all_models_likely %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "theta_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_likely_a <- ggplot(level1_likely, aes(x = .value, y = fct_rev(title), fill = title)) +
  stat_halfeye(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "A") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_b <- ggplot(filter(level2_likely, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

plot_diff_likely_c <- ggplot(filter(level2_likely, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_likely_d <- ggplot(level3_likely, aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Difference in donation likelihood", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

```{r priors-amounts, fig.width=8, fig.height=1.5, out.width="100%"}
amount_nu <- ggplot(data = tibble(x = c(0, 200)), aes(x = x)) +
  geom_area(stat = "function", fun = dexp, args = list(rate = 1/29), 
            fill = "grey80", color = "black") +
  labs(x = expression(Normality ~ parameter ~ (nu)), y = "Density") +
  annotate(geom = "label", x = 100, y = 0.009, 
           label = "Exponential(1/29)", size = pts(9)) +
  theme_ngos(base_size = 9, density = TRUE)

@@

```{r plot-amount-diffs, warning=FALSE, fig.width=4.75, fig.height=5.5, out.width="90%"}
all_models_amount <- all_models_amount %>% 
  # The `group` and `tidy` columns in each of these nested models contain
  # ordered factors, but we can't combine them with unnest() directly because
  # they have different levels (crackdown, issue, and funding), so we need to
  # make them unordered factors before unnesting
  mutate(posterior_chains_long = map(
    posterior_chains_long, ~mutate(., group = factor(group, ordered = FALSE)))
  ) %>% 
  mutate(tidy = map(
    tidy, ~mutate(., group = factor(group, ordered = FALSE)))
  )

tidied_diffs_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "mu_diff") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown"))

@@

plot_diff_amount_a <- ggplot(level1_amount, aes(x = .value, y = fct_rev(title), fill = title)) +
  geom_vline(xintercept = 0) +
  stat_halfeye(.width = c(0.8, 0.95)) +
  scale_x_continuous(labels = dollar) +
  scale_fill_manual(values = ngo_cols(c("blue", "red", "orange"), name = FALSE), guide = FALSE) +
  labs(x = "Difference in amount donated", y = NULL, tag = "A") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_b <- ggplot(filter(level2_amount, condition == "Issue"), 
                             aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("red", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = NULL, y = NULL, tag = "B") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

plot_diff_amount_c <- ggplot(filter(level2_amount, condition == "Funding"), 
                             aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("orange", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "C") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

plot_diff_amount_d <- ggplot(level3_amount, aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95), fill = ngo_cols("green", name = FALSE)) +
  geom_vline(xintercept = 0) +
  scale_x_continuous(labels = dollar) +
  labs(x = "Difference in amount donated", y = NULL, tag = "D",
       caption = "Point shows posterior median; thick black lines show 80% credible interval;\nthin black lines show 95% credible interval") +
  facet_wrap(~ facet_title, scales = "free_y") +
  theme_ngos(base_size = 8) +
  theme(panel.grid.major.y = element_blank())

@@

```{r amount-effect-size, warning=FALSE, out.width="80%"}
# Effect size
# (μ₁ - μ₂) / sqrt( (σ₁² + σ₂²) / 2)
tidied_eff_size_amount <- all_models_amount %>% 
  unnest(posterior_chains_long) %>% 
  filter(.variable == "cohen_d") %>% 
  mutate(category = case_when(
    str_count(title, "\\|") == 0 ~ "Level 1",
    str_count(title, "\\|") == 1 ~ "Level 2",
    str_count(title, "\\|") == 2 ~ "Level 3"
  )) %>% 
  mutate(title = str_remove(title, " \\| Crackdown")) %>% 
  mutate(title = fct_inorder(title))

@@

ggplot(tidied_eff_size_amount, aes(x = .value, y = fct_rev(title))) +
  stat_halfeye(.width = c(0.8, 0.95)) +
  geom_vline(xintercept = 0, size = 1) +
  geom_vline(xintercept = c(0.2, -0.2), linetype = "dotted", size = 0.5) +
  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
  geom_vline(xintercept = c(0.5, -0.5), linetype = "dotted", size = 0.5) +
  coord_cartesian(xlim = c(-1, 1)) +
  labs(x = "Cohen's d (effect size)", y = NULL) +
  theme_ngos()
```

### 2020-10-01 analysis/03_additional-analysis.Rmd
Clean up code to work with dplyr 1.0 and friends

---
title: "Additional analysis"
author: "Andrew Heiss and Suparna Chaudhry"
date: "Last run: `r format(Sys.time(), '%B %e, %Y')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(crackdownsphilanthropy)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(glue)
library(grid)
library(gridExtra)
library(Gmisc)
library(pander)
library(scales)
library(ipumsr)
library(huxtable)
library(here)

@@

```{r show-save-consort, fig.width=10, fig.height=6}
# Ordinarily, you can use grid.grab() to save the output of a grid figure into
# an object and then use that in ggsave(). However, when knitting, this creates
# a duplicate plot, which is frustrating. So instead, we use walk() to reprint
# all the grobs within specific pdf and png devices
#
# See https://stackoverflow.com/a/17509770/120898 for a similar issue

@@

  tidied <- tidyMCMC(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
                     estimate.method = "median", conf.method = "HPDinterval") %>%
    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))

@@

```{r avg-time-plot, fig.height=2.5, fig.width=4}
summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
  gtable::gtable_add_grob(., grobs = rectGrob(gp = gpar(fill = NA, lwd = 1)),
                          t = 1, b = nrow(.), l = 1, r = ncol(.))

@@

>>>>

---
title: "Additional analysis"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
output: 
  html_document:
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.retina = 3, fig.align = "center")
```

```{r load-libraries-data, warning=FALSE, message=FALSE}
# Load libraries
library(tidyverse)
library(crackdownsphilanthropy)
library(magrittr)
library(rstan)
library(rstanarm)
library(broom)
library(broom.mixed)
library(glue)
library(grid)
library(gridExtra)
library(Gmisc)  # For the CONSORT diagram
library(pander)
library(scales)
library(ipumsr)
library(huxtable)
library(here)

@@

```{r show-save-consort, fig.width=10, fig.height=6, out.width="100%"}
# Ordinarily, you can use grid.grab() to save the output of a grid figure into
# an object and then use that in ggsave(). However, when knitting, this creates
# a duplicate plot, which is frustrating. So instead, we use walk() to reprint
# all the grobs within specific pdf and png devices
#
# See https://stackoverflow.com/a/17509770/120898 for a similar issue

@@

  tidied <- tidy(mcmc_samples, conf.int = TRUE, conf.level = 0.95, 
                 estimate.method = "median", conf.method = "HPDinterval") %>%
    mutate(in_hpdi = (population_value >= conf.low & population_value <= conf.high))

@@

```{r avg-time-plot, fig.height=2.5, fig.width=4, out.width="80%"}
summary_stats <- tableGrob(time_summary, rows = NULL, theme = theme_ngos_table) %>% 
  gtable::gtable_add_grob(., grobs = rectGrob(gp = gpar(fill = NA, lwd = 1)),
                          t = 1, b = nrow(.), l = 1, r = ncol(.))

@@

\

### 2020-10-01 analysis/index.Rmd
Clean up code to work with dplyr 1.0 and friends

---
title: "NGO Crackdowns and Philanthropy"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

@@

State crackdown on non-governmental organizations (NGOs), particularly through legal restrictions on funding, has become increasingly common. How do legal restrictions on NGOs impact patterns of private philanthropic giving and individual donor decision-making? With reduced funding for NGOs working on contentious issues, and an absence of philanthropic culture in many developing countries, many NGOs rely on funds from private donors in Western countries. Using a survey experiment, we explore how this crackdown changes donors' preferences based on the issue area and funding sources of the NGO. We find that private donors are responsive to the legal difficulties international NGOs face abroad and are more likely to donate to legally besieged privately funded human rights NGOs. Additionally, already-likely donors give substantially more to legally restricted NGOs working on humanitarian issues. We conclude by discussing the implications for the sustainability of NGOs working abroad.

>>>>

---
title: "Dynamics of International Giving: How Heuristics Shape Individual Donor Preferences"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
---

@@

State restrictions on non-governmental organizations (NGOs) have become increasingly pervasive across the globe. While this crackdown has been shown to have a negative impact on public funding flows, we know little about how it impacts private philanthropy. How does information about crackdown abroad, as well as organizational attributes of nonprofits affect individual donors’ willingness to donate internationally? Using a survey experiment, we find that learning about repressive NGO environments increases generosity in that already-likely donors are willing to donate substantially more to legally besieged nonprofits. This generosity persists when mediated by two organizational-level heuristics: NGO issue areas and main funding sources. We discuss the implications of our results on how nonprofits can use different framing appeals to increase fundraising at a time when traditional public donor funding to such organizations is decreasing.

### 2020-10-01 analysis/preregistration.Rmd
HUGE reorganization (go to 0290370 for previous history)
Switched this to build as a package using rrtools, with pre-built Stan binaries through rstantools. As a result, everything got shuffled around, and GitHub doesn't use --follow in their logs, so the history is hidden. Going to 02903709c87b79e8a945dd31fafd2484cbf2bc7b and going back in history from there will let you see past changes to these files.

In general, here's what happened:

- All analysis files in the project root (Rmd files that generated the website) are now in /analysis/*
- R functions that lived in lib/* are now standalone

---
title: "Preregistration, design, IRB"
date: "Last run: `r format(Sys.time(), '%F')`"
bibliography: manuscript/bibliography.bib
---

>>>>

---
title: "Preregistration, design, IRB"
author: "Suparna Chaudhry and Andrew Heiss"
date: "Last run: `r format(Sys.time(), '%F')`"
bibliography: ../manuscript/bibliography.bib
---
